\documentclass[12pt,a4paper]{article}
\usepackage[latin1]{inputenc}
\usepackage{amsmath,setspace}
\usepackage{amsfonts}
\usepackage{amssymb} 
\usepackage{graphics}
\usepackage[left=1.00cm, right=1.00cm, top=1.00cm, bottom=1.00cm]{geometry}
\begin{document}
\begin{center}
Maharashtra State Board of Secondary and Higher Secondary Education, Pune. \\
Specimen Question Paper  \doublespacing \\
Subject : Mathematics and Statistics (Arts and Science)(40)\\
Time 3 Hrs.\hspace {4cm} \textbf{Class : XII} \hspace {4cm}Max. Marks 80
\end{center}

Note : 
\begin{enumerate}
\item All questions are compulsory.
\item The question paper consist of 30 questions divided into four sections A, B, C, D.
\item 
Section A contains 6 questions of 1 mark each.  \doublespacing\\
Section B contains 8 questions of 2 marks each.\\
Section C contains 6 questions of 3 marks each.\\
Section D contains 10 questions of 4 marks each.
\item Use of logarithmic tables is allowed. 
\item Use of calculator is \textbf{not} allowed.
\item For LPP only rough sketch is expected.Graph paper is not necssary.
\end{enumerate}
Select and write the most appropriate answer from the given alternative for each subquestions. 
\begin{enumerate}
\item $ p\rightarrow (q \rightarrow r) $ is logically equivalent to . . . \doublespacing \\
a) $ (p\vee q)\rightarrow \sim r $ \hspace{1cm} 
b) $ (p\wedge q)\rightarrow \sim r $ \hspace{1cm} 
c) $ (p\vee q)\rightarrow r $ \hspace{1cm}
d) $ (p\wedge q)\rightarrow r $  
\item If vectors $ a\hat{i}+\hat{j}+\hat{k}, \hat{i}+b\hat{j}+\hat{k}, \hat{i}+\hat{j}+c\hat{k} $ are coplanar then $ a+b+c-abc= $ . . .\\
a) $ -2 $ \hspace{1cm} 
b) $ -1 $ \hspace{1cm} 
c) $ 2 $ \hspace{1cm}
d)   $ 1 $
\item The angle between a diagonal of a cube and a diagonal of a face of a cube is . . . \\
a) $ \cos^{-1}(\frac{2}{3}) $ \hspace{1cm} 
b) $ \cos^{-1}(\frac{1}{3}) $ \hspace{1cm} 
c) $ \cos^{-1}\sqrt{\frac{2}{3}} $ \hspace{1cm}
d)$ \cos^{-1}\sqrt{\frac{1}{3}} $   
\item If $ x^2y^2=\tan^(-1){\sqrt{x^2+y^2}} $ then $ \frac{dy}{dx} $ = . . .\\  
a) $ -\frac{y}{x} $ \hspace{1cm} 
b)  $  \frac{y}{x} $\hspace{1cm} 
c)   $\frac{x}{y} $\hspace{1cm}
d)    $-\frac{x}{y} $
\item If the antiderivative of $ f(x)  $ is $ e^x $ and that of $ g(x) $ is $ \cos x $ then $ \int f(x) \cos x dx + \int g(x) e^x dx$ is . . . \\
a) $ f(x).g(x)+c $ \hspace{1cm} 
b)  $ f(x)+g(x) +c$\hspace{1cm} 
c) $ -e^x \cos x +c$ \hspace{1cm}
d) $ e^x \cos x +c$  
\item The differential equation of the family of lines where length of the normal from the origin to the line is $ p $ and inclination of the normal is $ \alpha $, is . . .\\
a) $ \frac {d^2y}{dx^2}= \cot \alpha $ \hspace{1cm} 
b) $ \frac {d^2y}{dx^2} $=0 \hspace{1cm} 
c) $ \frac {dy}{dx}= \cot \alpha $ \hspace{1cm}
d)   $ \frac {dy}{dx}= -\cot \alpha $ 

\begin{center}
\textbf {Section B} ( 16 marks)
\end{center}
\item Write the converse and the inverse of the conditional statement :  " If a sequence is bounded then it is convergent." 
\item Prove that the general solution of $ \cot \theta = \cot \alpha $ is $ \theta = 2n \pi \pm \alpha $
\item In $ \triangle ABC $ if $ \sin^2 A+\sin^2B=\sin^2C $ then show that teh triangle is a right angled triangle. 
\item Find the measure of the acute angle between the lines whose direction ratios are $ 1,2,2 $ and $ -3, 6,2 $. 
\item Differentiate $ \log (1+x^2)$ with respect to $ \tan^{-1}x $.
\item If the line $ y=4x-5  $ touches the curve $ y^2=ax^3+b $ at point $ (2, 3) $ then find the values of $ a $ and $ b $. 
\item Evaluate $ \int \frac {\cos (x+a)}{\cos x} dx $.
\item Evaluate \[ \int_{-\frac{-\pi}{2}}^{\frac{-\pi}{2}} \log (\frac {2-\sin x}{2+ \sin x} ) dx \]. 


\begin{center}
\textbf {Section C} ( 18 marks)
\end{center}


\textbf {Section D} ( 40 marks)

\end{enumerate}
\end{document}