\documentclass[12pt,a4paper]{article}

\usepackage[a4paper, portrait, top=1cm, left=20mm, bottom=2cm, right=1.5cm]{geometry}

\usepackage {amsmath}
\usepackage {amsfonts}
\usepackage {amssymb}
\usepackage {nccmath}
\usepackage {tasks}
\begin{document}

\begin{center}
\textbf {X. Y. Z. SCIENCE/COMMERCE/ARTS JUNIOR COLLEGE } \\
\textbf{MATHEMATICS} \\

Time : 3 Hrs \hspace {3.6cm} \textbf {FYJC - SCIENCE}  \hspace{2.9cm} Max. Marks : 80

\end{center}

Note :

\begin {itemize}
\item  All questions are compulsory 

\item Use of log table is allowed. Use of calculators is \textbf{NOT} allowed

\item Figures to the right indicate full marks.

\item The question paper consists of 30 questions divided in to \textbf{FOUR} sections A, B, C and D. 

\begin {itemize}

\item Section A contains  6 questions of 1 mark each.

\item Section B contains  8 questions of 2 marks each.

\item Section C contains  6 questions of 3 marks each.

\item Section D contains 10 questions of 4 marks each.

\end{itemize}

\item Graph paper is not necessary for problems on Linear Inequations. Rough graph is accepted.

\item In case of MCQ (Q1 to Q6) Evaluation would be done for the uncancelled first attempt only. 

\end{itemize}

% .... SECTION A Starts here ..

\begin{center}

\textbf {Section : A}

\end{center}

\settasks{counter-format={(tsk[A])}}

\begin {enumerate}

\item The value of $p$ if (4, $p$) lies on the curve $y^2 = 9x$ then the value(s) p =  

\begin{tasks}(4)
\task\ $\pm 4$
\task\ $\pm 6$
\task\ $\pm \frac{3}{2} $
\task\ $ 8$
\end{tasks}

\item The equation of the circle with center at (2, 3) and radius 5 units is 

\begin{tasks}(2)
\task\ $x^2+y^2-4x-6y-12=0$
\task\ $x^2+y^2+4x+6y-12=0$
\task\ $x^2+y^2-4x-6y+12=0$
\task\ $x^2+y^2+4x+6y+12=0$
\end{tasks}

\item

\item

\item

\item There are seven boys and 5 girls who are to be arranged in a row ....

% ... SECTION A Ends here ....

% ... SECTION B Starts here ..

\begin{center}

\textbf {Section : B}

\end{center}

\item Three cards are drawn at random ....

\item

\item Find the equation of the circle with center at (2, -7) and passing through (1, 3). 

\begin{center}
\textbf {OR}
\end{center}
Find center and radius of the circle $ x^2 + y^2 -6x + 8y - 11 = 0$

\item

\item

\item

\item

\item Find

% .... SECTION B Ends here ....

% ... SECTION C Starts here ...

\begin{center}

\textbf {Section : C}

\end{center}

\item Find 

\item

\item

\item

\item

\item Find the values of 

% .... SECTION C Ends here ....

% ... SECTION D Starts here ..

\begin{center}

\textbf {Section : D}

\end{center}

\item Find the equation of

\item

\item

\item

\item

\item

\item 

\item

\item

\item

\end{enumerate}

% .... SECTION D Ends here ....

\end{document}