\documentclass[14pt]{article}
\usepackage[a4paper, total={7.5in, 8in}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{paralist} 
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}
\setlength{\columnsep}{0.5cm}

\begin{document}
\begin{multicols}{2}
[
\section{Set Theory}
Note : This is test note, it will be spread over both columns. 
This is test note, it will be spread over both columns. 
This is test note, it will be spread over both columns. 
This is test note, it will be spread over both columns. 
]
\noindent
\begin{enumerate}
  
\item  If A = \{ 1, 2, 3, 4\}, B = \{3, 4, 5, 6\}
		  C = \{4, 5, 6, 7, 8\} and universal set  X = \{1, 2, 3, 4, 5, 6, 7, 8, 9, 10\}, then verify
the following:
i)		$ A \cup B\cap C) = (A\cup B) \cap (A \cup C)$

ii)	$A\cap (B\cup C)=(A\cap B)\cup (A \cup C)$
iii) $(A\cup B)' = (A'\cap B)'         $
iv)	$ (A\cap B)' = A'\cup B'          $
v)	$	 A = (A\cap B)\cup (A\cap B') $
vi)	$	 B = (A\cap B)\cup (A'\cap B) $
vii) $(A\cup B)=(A-B)\cup (A\cap B)\cup (B-A)$
Since $n(A \cap B)  \leq n(A),n(A\cap B)\leq n(B)$, then
viii)	$A \cap (B\delta C) = (A\cap B) \delta (A\cap C)$
ix) $n (A\cup B) = n(A) + n(B) - n(A\cap B)$
x) $n (B) = (A'\cap B) + n(A\cap B)$

\item If A and B are subsets of the universal set X and n(X) = 50, n(A) = 35, n(B) = 20,$ n(A'\cap B') = 5,$ find i) $n (A\cup B)$ ii) $n(A\cap B)$
iv) $ n(A\cap B')$
iii) $ n(A'\cap B) $

\item In a class of 200 students who appeared
certain examinations, 35 students failed
in CET, 40 in NEET and 40 in JEE,
20 failed in CET and NEET, 17 in NEET
and JEE, 15 in CET and JEE and 5 failed
in all three examinations. Find how many
students,
i)	did not fail in any examination.
ii) failed in NEET or JEE entrance.
		 
		 
\item In a hostel, 25 students take tea, 20 students
take coffee, 15 students take milk, 10
student take bot tea and coffee, 8 students
take both milk and coffee. None of them
take tea and milk both and everyone takes
atleast one beverage, find the total number
of students in the hostel.

\item If $P = \{1, 2, 3 \} $ and $Q = \{14 \}$,find sets $P \times Q $ and $Q \times P$

\item Let A = \{1, 2, 3, 4\}, B = \{4, 5, 6\}, C = \{ 5, 6 \}.
 Verify, i) $A \times (B \cap C) = (A \times B) \cap (A \times C)$				
ii) $ A \times (B \cup C) = (A \times B) \cup (A \times C)$

\item Let A = \{6, 8\} and B = \{1, 3, 5\} Show that $ R_1 = \{ (a, b) / a \in A, b\in B, a - b$
is an even number \} is a null relation.
$R_2 = \{(a, b)/a \in A, b \in B$, a+b is odd number \}
is an universal relation.
\end{enumerate} 
\end{multicols}
 
\end{document}