\documentclass[14pt]{article}
\usepackage[a4paper, total={7.5in, 10.5in}]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{paralist} 
\usepackage{multicol}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumitem}
\usepackage{textcomp}


\newcommand{\degree}{$^{\circ}\ $} %added space after degree

\setlength{\columnsep}{0.5cm}

\begin{document}
\centering 
{\huge \bf Mathematics QB For U2 - M1\par}
\vspace{1cm}
\begin{multicols}{2}

%%/////////////////////////////////
\section{Circle}
\noindent
\begin{enumerate}[resume]
 \item Find the equation of the circle with
(i) Centre at origin and radius 4.
(ii) Centre at (-3, -2) and radius 6.
\item Find the centre and radius of the circle.
(i) $x^2 + y^2 = 25$ (ii) $\left(x -\frac{1}{2}\right)^2 + \left(y +\frac{1}{3}\right)^2 = \frac{1}{36}$
\item Find the equation of the circle if the equations of two diameters are $2x + y = 6$ and $3x + 2y = 4$ and the radius of circle is 9.
\item Find the equation of a circle passing through the origin and having intercepts 4 and -5 on
the co-ordinate axes.

\item Find the equation of a circle passing through the points (1,-4), (5, 2) and having its centre on the line $x-2y+9 =0$.

\item Find the centre and radius of the circle $x^2 + y^2 - 6x - 8y - 24 = 0$ 

\item Find the centre and radius of the circle $x^2 + y^2 - x +2y - 3 = 0$ 

\item Find the equation of the circle passing through the points (5, 7), (6, 6) and (2, -2).

\item If the circle passes through the points (0, 0), (a, 0) and (0, b), find the co-ordinates of its centre.

\end{enumerate} 


%////////////////////////////////////
\section{Mesures of Dispersion}
\noindent
\begin{enumerate}[resume]


\item Compute range for the following data:

\begin{tabular}{|c|*{11}{c|}}
\hline Classes & 62-64 & 64-66 & 66-68 & 68-70 & 70-72  \\
\hline Frequency  & 5 & 3 & 4 & 5 & 3 \\
\hline
\end{tabular}


\item Find variance and S.D. for the following set of numbers 65, 77, 81, 98, 100, 80, 129

\item Compute variance for the following data:

\begin{tabular}{|c|*{11}{c|}}
\hline Age in Years & 16 & 17 & 18 & 19 & 20 & 21  \\
\hline No. of Students  & 20 & 7 & 11 & 17 &30 & 15  \\
\hline
\end{tabular}

\item Compute variance and standard deviation for the following data:

\begin{tabular}{|c|*{11}{c|}}
\hline X & 2 & 4 & 6 & 8 & 10 & 12 & 14 & 16 & 18 & 20  \\
\hline F & 8 & 10 & 10 & 7 & 6 & 6 & 3 & 4 & 2 & 6 \\
\hline
\end{tabular}

\item Compute variance and standard deviation :

\begin{tabular}{|c|*{9}{c|}}
\hline X & 31 & 32 & 33 & 34 & 35 & 36 & 37 \\
\hline F & 15 & 12 & 10 & 8 & 9 & 10 & 6 \\
\hline
\end{tabular}

\item The means of two samples of sizes 60 and 120 respectively are 35.4 and 30.9 and the standard deviations 4 and 5. Obtain the standard deviation of the sample of size 180 obtained by combining the two sample.


\item For a certain data, following information is available.

\begin{tabular}{|c|*{9}{c|}}
\hline  & X & Y  \\
\hline Mean & 13 & 17  \\
\hline S.D. & 3 & 2  \\
\hline Size & 20 & 30  \\
\hline
\end{tabular}\\
\vspace{1mm}
Obtain the combined standard deviation.

\item A group of 65 students of class XI have their average height is 150.4 cm with coefficient of variance 2.5\%. What is the standard deviation of their height?


\item Given below is the information about marks obtained in Mathematics and Statistics by 100 students in a class. Which subject shows
the highest variability in marks?
\begin{tabular}{|c|*{9}{c|}}
\hline  & Mathematics & Statistics \\
\hline Mean & 20 & 25  \\
\hline S.D. & 2 & 3  \\
\hline
\end{tabular}\\

\end{enumerate} 



\end{multicols}
 
\end{document}